---
title: "README"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SIGMA: A clusterability measure for scRNA-seq data
A package to calculate clusterability in clusters of scRNA-seq data. By applying this measure you can assess if meaningful variability is left in clusters.


## Installation
```{r}
# install.packages("devtools")
devtools::install_github("Siliegia/SIGMA")
```

## Example

This how you can use the functions in this R package. The most important one is sigma_funct, which calculates the clusterability per cluster. 

```{r}
library(SIGMA)
library(splatter)
library(ggplot2)

#Load sample data simulated with splatter
data("splatO")

expr <- counts(splatO)
expr <- expr[rowSums(expr)>0,]

#Normalize and log-transform the data
expr.norm <- t(t(expr)/colSums(expr))*10000
expr.norm.log <- log(expr.norm + 1)

#Create toy example of a data set
test.cluster <- as.character(splatO$Group)
test.cluster[test.cluster == "Group3"] <- "Group2"
test.cluster[test.cluster == "Group4"] <- "Group2"

#Main funcion that calculates the clusterability
out <- sigma_funct(expr = expr.norm.log, clusters = test.cluster, exclude = data.frame(clsm = log(colSums(expr) + 1)))
```

For ways to evaluate the results of this clusterability measure check out the vignette Guide_to_sigma.
